Articles_Plots

### 2022-06-02 Articles.Rmd
update colors for the plots

Identical_ro$Model<-recode_factor(Identical_ro$Model,
                                  `RS DM`="Random Sampling: Data Model",
                                  `RS AM 1`="Random Sampling: Incorrect Model 1",
                                  `RS AM 2`="Random Sampling: Incorrect Model 2",
                                  `RS AM 3`="Random Sampling: Incorrect Model 3",
                                  `mMSE DM`="Optimal Sub-sampling mMSE: Data Model",
                                  `mMSE AM 1`="Optimal Sub-sampling mMSE: Incorrect Model 1",
                                  `mMSE AM 2`="Optimal Sub-sampling mMSE: Incorrect Model 2",
                                  `mMSE AM 3`="Optimal Sub-sampling mMSE: Incorrect Model 3",
                                  `mVc DM`="Optimal Sub-sampling mVc: Data Model 1",
                                  `mVc AM 1`="Optimal Sub-sampling mVc: Incorrect Model 1",
                                  `mVc AM 2`="Optimal Sub-sampling mVc: Incorrect Model 2",
                                  `mVc AM 3`="Optimal Sub-sampling mVc: Incorrect Model 3",
                                  `mMSE MR`="Model Robust Optimal Sub-sampling mMSE: Data Model",
                                  `mVc MR`="Model Robust Optimal Sub-sampling mVc: Data Model")

@@

Colors_mMSE<-c("#88CCEE", #"#A6C3D3","#5D92B0","#35586C", 
               "#FFC4D8","#E28490","#BB2C3E","#55141C",
               "#DDCC77")

Selected_Models_mVc<-c("Random Sampling: Data Model",
                       #"Random Sampling: Incorrect Model 1",
                       #"Random Sampling: Incorrect Model 2",
                       #"Random Sampling: Incorrect Model 3",
                       "Optimal Sub-sampling mVc: Data Model 1",
                       "Optimal Sub-sampling mVc: Incorrect Model 1",
                       "Optimal Sub-sampling mVc: Incorrect Model 2",
                       "Optimal Sub-sampling mVc: Incorrect Model 3",
                       "Model Robust Optimal Sub-sampling mVc: Data Model")

Colors_mVc<-Colors_mVc<-c("#88CCEE",#"#A6C3D3","#5D92B0","#35586C", 
                          "#FFC4D8","#E28490","#BB2C3E","#55141C", 
                          "#DDCC77")

>>>>

Identical_ro$Model<-recode_factor(Identical_ro$Model,
                                  `RS DM`="Random Sampling: Data Model",
                                  `RS AM 1`="Random Sampling: Incorrect Model 1",
                                  `RS AM 2`="Random Sampling: Incorrect Model 2",
                                  `RS AM 3`="Random Sampling: Incorrect Model 3",
                                  `mMSE DM`="Optimal Sub-sampling mMSE: Data Model",
                                  `mMSE AM 1`="Optimal Sub-sampling mMSE: Incorrect Model 1",
                                  `mMSE AM 2`="Optimal Sub-sampling mMSE: Incorrect Model 2",
                                  `mMSE AM 3`="Optimal Sub-sampling mMSE: Incorrect Model 3",
                                  `mVc DM`="Optimal Sub-sampling mVc: Data Model",
                                  `mVc AM 1`="Optimal Sub-sampling mVc: Incorrect Model 1",
                                  `mVc AM 2`="Optimal Sub-sampling mVc: Incorrect Model 2",
                                  `mVc AM 3`="Optimal Sub-sampling mVc: Incorrect Model 3",
                                  `mMSE MR`="Model Robust Optimal Sub-sampling mMSE: Data Model",
                                  `mVc MR`="Model Robust Optimal Sub-sampling mVc: Data Model")

@@

# Colors_mMSE<-c("#88CCEE", #"#A6C3D3","#5D92B0","#35586C", 
#                "#FFC4D8","#E28490","#BB2C3E","#55141C",
#                "#DDCC77")

Colors_mMSE<-c("black",#"grey","grey","grey",
              "#cc0000", 
              "#ff578a","#ff578a","#ff578a",
              "darkgreen")

Selected_Models_mVc<-c("Random Sampling: Data Model",
                       #"Random Sampling: Incorrect Model 1",
                       #"Random Sampling: Incorrect Model 2",
                       #"Random Sampling: Incorrect Model 3",
                       "Optimal Sub-sampling mVc: Data Model",
                       "Optimal Sub-sampling mVc: Incorrect Model 1",
                       "Optimal Sub-sampling mVc: Incorrect Model 2",
                       "Optimal Sub-sampling mVc: Incorrect Model 3",
                       "Model Robust Optimal Sub-sampling mVc: Data Model")

# Colors_mVc<-Colors_mVc<-c("#88CCEE",#"#A6C3D3","#5D92B0","#35586C", 
#                           "#FFC4D8","#E28490","#BB2C3E","#55141C", 
#                           "#DDCC77")

Colors_mVc<-c("black",#"grey","grey","grey",
              "#cc0000", 
              "#ff578a","#ff578a","#ff578a",
              "darkgreen")
